MCC Informativeness - summary pilots kids

### 2019-01-09 stats/kids/kids_summary_inf_pilot.Rmd
first draft CogSci paper

## round 1 adult design
d_round_1 <- read_csv(file="kids_inf.data.csv")%>%
  filter(trial != "train", control == "false")%>%
  mutate(setup = "table",
         move = "no_move",
         turn = "no_turn",
         wording = "there_is_a_dax",
         filler = "no_filler",
         choice = "object",
         subage = age,
         experiment = "1_round1",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)

@@

```{r plot, echo = FALSE, warning = FALSE, fig.width=12}

@@

ggplot() +
  geom_jitter(data = p, aes(x = 1, y = correct, col = subage, alpha = .2),width = .3,height = .025)+
  geom_pointrange(data = p1, aes(x = 1, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8)+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few() +
  facet_grid(subage~experiment)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

>>>>

## round 1 adult design
d_round_1 <- read_csv(file="../data/kids_inf.data.csv")%>%
  filter(trial != "train", control == "false")%>%
  mutate(setup = "table",
         move = "no_move",
         turn = "no_turn",
         wording = "there_is_a_dax",
         filler = "no_filler",
         choice = "object",
         subage = age,
         experiment = "1_round1",
         subage = as.character(subage))%>%
  select(subid,subage,setup,control,trial,move,turn,wording,filler,choice,experiment,agent,correct)

@@

```{r plot, echo = FALSE, warning = FALSE, fig.width=12, fig.height=3}

@@

ggplot() +
  geom_jitter(data = p, aes(x = 1, y = correct, col = subage, alpha = .2), position = position_jitterdodge(jitter.width = 0.05, jitter.height = 0.05, dodge.width = 0.5))+
  geom_pointrange(data = p1, aes(x = 1, y = mean, col = subage, ymin = ci_lower, ymax = ci_upper),size = .8, position = position_dodge(width = 0.5))+
  geom_hline(yintercept = 0.5, lty=2)+
  labs(x="",y="Proportion Expected Choice")+
  theme_few(base_size = 20) +
  facet_grid(~experiment)+
  ylim(-0.05,1.05)+
  guides(alpha = F)+ 
  theme(axis.text.x=element_blank(),axis.ticks.x=element_blank())
```

```{r}
ggsave("../graphs/kids_inf_pilot.png", width = 12, height = 3, scale = 1.5)
```
